Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2020-01-31 doc/Paper/main.tex
Fixed redshift bin numbering.

    Finally, we compute the super-sample covariance contribution following the treatment of \cite{Krause:2017}, i.e.:
     \begin{equation}
    \begin{aligned}
       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) &= \int \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
    \end{aligned}
    \end{equation}
        The quantity $\sigma_b^2(z)$ is the variance of the long wavelength mode $\delta_{\rm LS}$ over the survey footprint, given by
    \begin{equation}
      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
    \end{equation}
    Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set:
    \begin{equation}
      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
    \end{equation}
    where $J_1(x)$ is the cylindrical Bessel function of order 1.
    Finally, the quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g. \cite{Krause:2017}):
     \begin{equation}
    \begin{aligned}
      \frac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} =& \left( \frac{68}{21} - \frac{1}{3}\frac{\mathrm{d}\log{k^{3} P_{\mathrm{lin}}}(k, z)}{\mathrm{d}\log k} \right) I_{a}^{1}(k)I_{b}^{1}(k)P_{\mathrm{lin}}(k, z) + I_{ab}^{1}(k, k) \\ &- (b_{a} + b_{b})P_{ab}(k, z).
    \label{eq:ps-resp}  
    \end{aligned}
     \end{equation}
    The last term in Eq.~\ref{eq:ps-resp} accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.

@@

  \subsection{Covariance matrix}\label{ssec:results.covariance}
    We compute the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}. In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions. As can be seen, the Gaussian contribution is dominant on large scales while the non-Gaussian part becomes important at small scales and low redshift. The high redshift bins are mostly insensitive to non-Gaussian contributions to the covariance. Finally, the SSC is subdominant in all cases. This is mainly due to the number density correction in Eq.~\ref{eq:ps-resp}, which significantly suppresses any SSC contributions to the total covariance.
    \begin{figure}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, computed analytically as described in Sec.~\ref{sssec:methods.theory.covar}. \rev{The indices denote redshift bins, e.g. the sub-covariance matrix with indices 00-00 denotes $\mathrm{Cov}(C^{00}_{\ell}, C^{00}_{\ell'})$, 00-01 denotes $\mathrm{Cov}(C^{00}_{\ell}, C^{01}_{\ell'})$ etc.}}\label{fig:covmat}
      \end{center}
    \end{figure}

    \begin{figure}
      \begin{center}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}
        \caption{$C_{\ell}^{00}$}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf} \\
        \caption{$C_{\ell}^{11}$}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}
        \caption{$C_{\ell}^{22}$}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}
        \caption{$C_{\ell}^{33}$}
        \end{subfigure}
        \caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} \label{fig:covariance-contributions}
      \end{center}
    \end{figure}

@@

            bins = 0, 1, 2 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.4\pm 2.3$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.6\substack{+2.9 \\ -2.8}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
            bins = 1, 2, 3 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.2\pm 2.9$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.5\substack{+3.7 \\ -3.6}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\

>>>>

    Finally, we compute the super-sample covariance contribution following the treatment of \cite{Krause:2017}, i.e.:
     \begin{equation}
    \begin{aligned}
       \mathrm{Cov}_{\mathrm{SSC}}(C^{ab}_{\ell}, C^{cd}_{\ell'}) &= \int \mathrm{d}\chi \;\frac{q^{a}(\chi)q^{b}(\chi)q^{c}(\chi)q^{d}(\chi)}{\chi^{4}} \times \\ &\frac{\partial P_{ab}(\sfrac{\ell}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\frac{\partial P_{cd}(\sfrac{\ell'}{\chi}, z(\chi))}{\partial \delta_{\rm LS}}\sigma^{2}_{b}(z(\chi)).
    \end{aligned}
    \end{equation}
        The quantity $\sigma_b^2(z)$ is the variance of the long wavelength mode $\delta_{\rm LS}$ over the survey footprint, given by
    \begin{equation}
      \sigma_b^2(z) = \int \frac{\mathrm{d}k_\perp^2}{(2\pi)^2}P_{\rm lin}(k_\perp,z)\left|W(k_\perp,z)\right|^2.
    \end{equation}
    Furthermore $W(k_\perp,z)$ denotes the Fourier transform of the survey footprint, which we approximate as a compact circle with an area matched to our data set\footnote{\rev{We expect this approximation to be acceptable for the present analysis as HSC covers a small sky fraction and we mainly consider large angular multipoles (see e.g. Refs.~\cite{Krause:2017a, Barreira:2018}).}}:
    \begin{equation}
      W(k_\perp,z)=\frac{2 J_1(k_\perp\chi(z)\theta_s)}{k_\perp \chi(z)\theta_s},\hspace{12pt} \theta_s={\rm arccos}(1-2f_{\rm sky}),
    \end{equation}
    where $J_1(x)$ is the cylindrical Bessel function of order 1.
    Finally, the quantity $\partial P_{ab}(k, z)/\partial \delta_{\rm LS}$ is the response of the power spectrum $P_{ab}$ to a large-scale density fluctuation, which we estimate using the halo model and results from perturbation theory as (e.g. \cite{Krause:2017}):
     \begin{equation}
    \begin{aligned}
      \frac{\partial P_{ab}(k, z)}{\partial \delta_{\rm LS}} =& \left( \frac{68}{21} - \frac{1}{3}\frac{\mathrm{d}\log{k^{3} P_{\mathrm{lin}}}(k, z)}{\mathrm{d}\log k} \right) I_{a}^{1}(k)I_{b}^{1}(k)P_{\mathrm{lin}}(k, z) + I_{ab}^{1}(k, k) \\ &- (b_{a} + b_{b})P_{ab}(k, z).
    \label{eq:ps-resp}  
    \end{aligned}
     \end{equation}
    The last term in Eq.~\ref{eq:ps-resp} accounts for the fact that the observed galaxy overdensity is computed using the mean galaxy density estimated inside the survey volume.

@@

  \subsection{Covariance matrix}\label{ssec:results.covariance}
    We compute the covariance matrix of all measured power spectra analytically as described in Sec.~\ref{sssec:methods.theory.covar} and the resulting correlation matrix is shown in Fig.~\ref{fig:covmat}. In Fig.~\ref{fig:covariance-contributions}, we split the auto-covariances for the four redshift bins into the Gaussian, non-Gaussian and SSC contributions. As can be seen, the Gaussian contribution is dominant on large scales while the non-Gaussian part becomes important at small scales and low redshift. The high redshift bins are mostly insensitive to non-Gaussian contributions to the covariance. Finally, the SSC is subdominant in all cases. This is mainly due to the number density correction in Eq.~\ref{eq:ps-resp}, which significantly suppresses any SSC contributions to the total covariance.
    \begin{figure}
      \begin{center}
        \includegraphics[width=0.5\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_G+NG+SSC.pdf}
        \caption{Correlation matrix for all auto- and cross-power spectra considered in our analysis, computed analytically as described in Sec.~\ref{sssec:methods.theory.covar}. \rev{The indices denote redshift bins, e.g. the sub-covariance matrix with indices 11-11 denotes $\mathrm{Cov}(C^{11}_{\ell}, C^{11}_{\ell'})$, 11-12 denotes $\mathrm{Cov}(C^{11}_{\ell}, C^{12}_{\ell'})$ etc.}}\label{fig:covmat}
      \end{center}
    \end{figure}

    \begin{figure}
      \begin{center}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=0.pdf}
        \caption{$C_{\ell}^{11}$}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=1.pdf} \\
        \caption{$C_{\ell}^{22}$}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=2.pdf}
        \caption{$C_{\ell}^{33}$}
        \end{subfigure}
        \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{figures/covmat_HSC_dg_hoddg_hodxdg_hoddg_hod_trisp=4h3h2h_SSC=LINBIAS-resp_l=ells_eff_all_wcross_clfit=HOD-zevol_culled=True_coadd=area_comparison=G+NG+SSC_bin=3.pdf}
        \caption{$C_{\ell}^{44}$}
        \end{subfigure}
        \caption{Comparison of the different contributions to the covariance matrix for the four auto-power spectra considered in our analysis.} \label{fig:covariance-contributions}
      \end{center}
    \end{figure}

@@

            bins = 1, 2, 3 & $\sfrac{44.4}{43}$ $(0.41)$ & $-0.4\pm 2.3$ & $11.88\substack{+0.22 \\ -0.23}$ & $0.6\substack{+2.9 \\ -2.8}$ & $13.09\substack{+0.27 \\ -0.28}$ & - & - & - \\
            bins = 2, 3, 4 & $\sfrac{44.4}{46}$ $(0.54)$ & $1.2\pm 2.9$ & $11.97\substack{+0.31 \\ -0.36}$ & $3.5\substack{+3.7 \\ -3.6}$ & $13.23\substack{+0.39 \\ -0.43}$ & - & - & - \\
